Simulations

### 2020-12-09 Simulations.Rmd
Improve visualization

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(ggplot2)
set.seed(400)
```

@@

nloop <- 10000
oldGap <- rep(NA, nloop)
newGap <- rep(NA, nloop)

@@

ggplot() +
  geom_histogram(aes(oldGap), col = 2, bins = 50) +
  geom_histogram(aes(newGap), col = 4, bins = 50)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(ggplot2)
library(plyr)
set.seed(410)
```

@@

nloop <- 1000
oldGap <- rep(NA, nloop)
newGap <- rep(NA, nloop)

@@

df <- data.frame(Rule_Type = rep(c("Old alignment & rules", "New alignment & rules"), each = nloop), gap = c(oldGap, newGap))
dfDat <- ddply(df, "Rule_Type", summarise, grp.mean=mean(gap))

ggplot(df, aes(x = gap, fill = Rule_Type)) +
  geom_density(alpha = 0.4) +
  geom_vline(aes(xintercept = mean(oldGap)), col = 4) +
  geom_vline(data = dfDat, aes(xintercept = grp.mean, color = Rule_Type), linetype = "dashed") +
  xlab("Conference gap") +
  ylab("Density")
